### 2013-06-19 Tex/chapters/model.tex
Autokorrelation etwas verbessert
kosmetischer eingriff
Einrückung im Quellcode verbessert

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    which will be described in more detail in section
    \ref{ssec:isingmodel}.\\
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
                \label{sfig:lunes:def}
                \input{images/GG_RNG_def}
        }
        \subfigure[Relative Neighborhood graph example][]{
                \label{sfig:lunes:rng}
                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \subfigure[Gabriel graph example][]{
                \label{sfig:lunes:gg}
                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
                    Graph (hatched region) and
                    Gabriel Graph (cross hatched region)
                 \subref{sfig:lunes:rng} Example of a Relative
                    Neighborhood Graph on periodic boundary conditions.
                    Periodic nodes are dashed.
                 \subref{sfig:lunes:gg} Example of a Gabriel Graph on
                    periodic boundary conditions. Periodic nodes are
                    dashed.
                }
        \label{fig:lunes}

@@

    For evaluation the Monte Carlo simulation is is run till the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetisation per site \(m\) and energy per site \(E\)
    are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
    denotes the \emph{autocorrelation time} after which two states of
    the system are not correlated anymore.
    For every observable \(O\) the expected value \(\avg{O}\) is averaged
    over different randomly generated lattices \(\overline{\avg{O}}\). The
    errors are estimated by bootstrapping.

@@

                {The Binder cumulant \(g\) of an square lattice Ising model

@@

    exact solution

@@

        T_c = 2J/\ln(1+\sqrt 2) = 2.2691... \cite{Onsager1944}

>>>>

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    which will be described in more detail in section
    \ref{ssec:isingmodel}.\\
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
            \label{sfig:lunes:def}
            \input{images/GG_RNG_def}
        }
        \subfigure[Relative Neighborhood graph example][]{
            \label{sfig:lunes:rng}
            \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \subfigure[Gabriel graph example][]{
            \label{sfig:lunes:gg}
            \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
        {
            \subref{sfig:lunes:def} Lunes of Relative Neighborhood
                Graph (hatched region) and
                Gabriel Graph (cross hatched region)
            \subref{sfig:lunes:rng} Example of a Relative
                Neighborhood Graph on periodic boundary conditions.
                Periodic nodes are dashed.
            \subref{sfig:lunes:gg} Example of a Gabriel Graph on
                periodic boundary conditions. Periodic nodes are
                dashed.
        }
        \label{fig:lunes}

@@

    For evaluation the Monte Carlo simulation is is run till the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetisation per site \(m\) and energy per site \(E\)
    are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
    denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
    For every observable \(O\) the expected value \(\avg{O}\) is averaged
    over different randomly generated lattices \(\overline{\avg{O}}\). The
    errors are estimated by bootstrapping.

@@

        {
            The Binder cumulant \(g\) of an square lattice Ising model

@@

    exact solution \cite{Onsager1944}

@@

        T_c = 2J/\ln(1+\sqrt 2) = 2.2691...
